Forecasting the 2024 US Presidential Election

### 2024-11-04 paper/paper.qmd
Completed the introduction section

*Results paragraph:* Summarize the key findings of the model, highlighting its predictive accuracy and implications.

>>>>

In our models, we identified eight pivotal swing states—Georgia, Michigan, Nevada, New Hampshire, North Carolina, Pennsylvania, and Wisconsin—crucial for predicting the 2024 election outcome. We constructed Bayesian generalized linear models to estimate the percentage likelihood of candidates Trump and Harris winning in these states, incorporating education level, gender distribution, ethnic demographics, historical voting patterns, approval ratings of Joe Biden, and current leanings toward Trump or Harris. Our election forecast resulted in 6 out of 8 pivotal states, as well as the national polling average, leaning towards the Republican party.
